### 2012-03-12 paper.tex
Bringing the lay-out back to match guidelines for PhysChem ChemPhys...

\documentclass[8.5pt,twoside,twocolumn]{article}
\oddsidemargin -1.2cm
\evensidemargin -1.2cm
\textwidth 18cm
\headheight 1.0in
\topmargin -3.5cm
\textheight 22cm
\usepackage[super,sort&compress,comma]{natbib} 
\usepackage[version=3]{mhchem}
\usepackage[utf8]{inputenc}
\usepackage{times,mathptmx}
% \usepackage{times}
% feel free not to use mathptmx if it causes difficulties
\usepackage{sectsty}
\usepackage{balance}

@@

%\thispagestyle{plain}
%\fancypagestyle{plain}{
%\fancyhead[L]{\includegraphics[height=8pt]{headers/LH}}
%\fancyhead[C]{\hspace{-1cm}\includegraphics[height=20pt]{headers/CH}}
%\fancyhead[R]{\includegraphics[height=10pt]{headers/RH}\vspace{-0.2cm}}
%\renewcommand{\headrulewidth}{1pt}}
%\renewcommand{\thefootnote}{\fnsymbol{footnote}}
%\renewcommand\footnoterule{\vspace*{1pt}% 
%\hrule width 3.4in height 0.4pt \vspace*{5pt}} 
%\setcounter{secnumdepth}{5}

@@

%\fancyfoot{}
%\fancyfoot[LO,RE]{\vspace{-7pt}\includegraphics[height=9pt]{headers/LF}}
%\fancyfoot[CO]{\vspace{-7.2pt}\hspace{12.2cm}\includegraphics{headers/RF}}
%\fancyfoot[CE]{\vspace{-7.5pt}\hspace{-13.5cm}\includegraphics{headers/RF}}
%\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
%\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
\fancyhead{}
\renewcommand{\headrulewidth}{1pt} 
\renewcommand{\footrulewidth}{1pt}
\setlength{\arrayrulewidth}{1pt}
\setlength{\columnsep}{6.5mm}
\setlength\bibsep{1pt}

\twocolumn[
  \begin{@twocolumnfalse}
\noindent\LARGE{\textbf{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure}}
\vspace{0.6cm}

\noindent\large{\textbf{Robert Jensen, Thomas Andersen, Anders Nierhoff, Thomas Pedersen, Ole Hansen, Søren Dahl and Ib Chorkendorff}}\vspace{0.5cm}
%Please note that \ast indicates the corresponding author(s) but no footnote text is required.

%\noindent\textit{\small{\textbf{Received Xth XXXXXXXXXX 20XX, Accepted Xth XXXXXXXXX 20XX\newline
%First published on the web Xth XXXXXXXXXX 200X}}}

%\noindent \textbf{\small{DOI: 10.1039/b000000x}}
\vspace{0.6cm}
%Please do not change this text.

@@

%Footnotes
%\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}

@@

%\footnotetext{\textit{$^{a}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
%\footnotetext{\textit{$^{b}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark}}

>>>>

\documentclass[8.5pt,twoside,twocolumn]{article}
\oddsidemargin -1.2cm
\evensidemargin -1.2cm
\textwidth 18cm
\headheight 1.0in
\topmargin -3.5cm
\textheight 22cm
\usepackage[super,sort&compress,comma]{natbib} 
\usepackage[version=3]{mhchem}
\usepackage[utf8]{inputenc}
\usepackage{times,mathptmx}
 \usepackage{times}
% feel free not to use mathptmx if it causes difficulties
\usepackage{sectsty}
\usepackage{balance}

@@

\thispagestyle{plain}
\fancypagestyle{plain}{
\fancyhead[L]{\includegraphics[height=8pt]{headers/LH}}
\fancyhead[C]{\hspace{-1cm}\includegraphics[height=20pt]{headers/CH}}
\fancyhead[R]{\includegraphics[height=10pt]{headers/RH}\vspace{-0.2cm}}
\renewcommand{\headrulewidth}{1pt}}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand\footnoterule{\vspace*{1pt}% 
\hrule width 3.4in height 0.4pt \vspace*{5pt}} 
\setcounter{secnumdepth}{5}

@@

\fancyfoot{}
\fancyfoot[LO,RE]{\vspace{-7pt}\includegraphics[height=9pt]{headers/LF}}
\fancyfoot[CO]{\vspace{-7.2pt}\hspace{12.2cm}\includegraphics{headers/RF}}
\fancyfoot[CE]{\vspace{-7.5pt}\hspace{-13.5cm}\includegraphics{headers/RF}}
\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
\fancyhead{}
\renewcommand{\headrulewidth}{1pt} 
\renewcommand{\footrulewidth}{1pt}
\setlength{\arrayrulewidth}{1pt}
\setlength{\columnsep}{6.5mm}
\setlength\bibsep{1pt}

\twocolumn[
  \begin{@twocolumnfalse}
\noindent\LARGE{\textbf{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure$^\dag$}}
\vspace{0.6cm}

\noindent\large{\textbf{Robert Jensen,\textit{$^{a}$} Thomas Andersen,\textit{$^{a}$} Anders Nierhoff,\textit{$^{a}$} Thomas Pedersen,\textit{$^{b\ddag}$} Ole Hansen,\textit{$^{b\ddag}$} Søren Dahl,\textit{$^{a\ddag}$} and Ib Chorkendorff\textit{$^{a}$}}}\vspace{0.5cm}
%Please note that \ast indicates the corresponding author(s) but no footnote text is required.

\noindent\textit{\small{\textbf{Received Xth XXXXXXXXXX 20XX, Accepted Xth XXXXXXXXX 20XX\newline
First published on the web Xth XXXXXXXXXX 200X}}}

\noindent \textbf{\small{DOI: 10.1039/b000000x}}
\vspace{0.6cm}
%Please do not change this text.

@@

%Footnotes
\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}

@@

\footnotetext{\textit{$^{a}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
\footnotetext{\textit{$^{b}$~CINF, Department of Micro- and Nanotechnology, Technical University of Denmark, Ørsteds Plads, B 345B, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
%\footnotetext{\textit{$^{b}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark}}
